Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-06-05 docs/00-manuscripts/ieee/ieee-manuscript.tex
clarify the usefulness of ML in this study
"invasive pathogens" -> "pathogens"

ML methods in combination with remote sensing data are used in many environmental fields such as vegetation cover analysis or forest carbon storage mapping \cite{mascaro2014, urban2018}.
The ability of predicting into unknown space qualifies these tools as a promising toolset for such tasks.
One aspect of this research field is to enhance the understanding of biotic and abiotic stress triggers, for example by analyzing tree defoliation \cite{hawrylo2018}.

@@

Airborne hyperspectral data with a spatial resolution of one meter and 126 spectral bands was available for four Monterey Pine (\textit{Pinus radiata D. Don}) plantations in northern Spain.
The trees in the plots suffer from infections of invasive pathogens such as \textit{Diplodia sapinea (Fr.) Fuckel}, \textit{Fusarium circinatum Nirenberg \& O'Donnell}, \textit{Armillaria mellea (Vahl) P. Kumm}, \textit{Heterobasidion annosum (Fr.) Bref}, \textit{Lecanosticta acicola (Thüm) Syd.} and \textit{Dothisthroma septosporum (Dorogin) M. Morelet} causing a spread of cankers or defoliation \cite{mesanza2016, iturritxa2017}.
The last two fungi are mainly responsible for the foliation loss of the trees analyzed in this study \cite{iturritxa2014}.
In-situ measurements of defoliation of trees (serving as a proxy for tree health) were collected to serve as the response variable \textit{defoliation} which ranges from 0 - 100 (in \%) (\autoref{fig:defol-distr}).

>>>>

ML methods in combination with remote sensing data are used in many environmental fields such as vegetation cover analysis or forest carbon storage mapping \cite{mascaro2014, urban2018}.
The ability of predicting into unknown space qualifies ML algorithms as a helpful tool for such environmental analyses.
One aspect of this research field is to enhance the understanding of biotic and abiotic stress triggers, for example by analyzing tree defoliation \cite{hawrylo2018}.

@@

Airborne hyperspectral data with a spatial resolution of one meter and 126 spectral bands was available for four Monterey Pine (\textit{Pinus radiata D. Don}) plantations in northern Spain.
The trees in the plots suffer from infections of pathogens such as \textit{Diplodia sapinea (Fr.) Fuckel}, \textit{Fusarium circinatum Nirenberg \& O'Donnell}, \textit{Armillaria mellea (Vahl) P. Kumm}, \textit{Heterobasidion annosum (Fr.) Bref}, \textit{Lecanosticta acicola (Thüm) Syd.} and \textit{Dothisthroma septosporum (Dorogin) M. Morelet} causing a spread of cankers or defoliation \cite{mesanza2016, iturritxa2017}.
The last two fungi are mainly responsible for the foliation loss of the trees analyzed in this study \cite{iturritxa2014}.
In-situ measurements of defoliation of trees (serving as a proxy for tree health) were collected to serve as the response variable \textit{defoliation} which ranges from 0 - 100 (in \%) (\autoref{fig:defol-distr}).
